---
title: "JSTP-Interval Estimation for Binomial Proportions Under Differential Privacy"
author: "KAO, HSUAN-CHEN(Justin)"
date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: xelatex
  html_document:
    df_print: paged
geometry: margin=0.5in
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
```

# Method: epsilon-DP: The code below is for n = 1000; for n = 100, please set n = 100.

## We set set.seed(12345) for all code to ensure reproducibility in the paper submitted to JSTP. Furthermore, the for loop takes a long time to run; therefore, using cache = TRUE is highly recommended for the main chunk.


### Wald and Wilson without Differential Privacy

```{r cache=TRUE}
library(dplyr)  

set.seed(12345)

wald_confidence_interval_no_dp <- function(p_hat, n, alpha = 0.05) {
  z_alpha <- qnorm(1 - alpha / 2)  
  var_p_hat <- (p_hat * (1 - p_hat)) / n
  lower_bound <- p_hat - z_alpha * sqrt(var_p_hat)
  upper_bound <- p_hat + z_alpha * sqrt(var_p_hat)
  return(c(lower_bound, upper_bound, upper_bound - lower_bound)) 
}

wilson_confidence_interval_no_dp <- function(p_hat, n, alpha = 0.05) {
  z_alpha <- qnorm(1 - alpha / 2)  
  A <- n + z_alpha^2
  B <- -(2 * n * p_hat + z_alpha^2)
  C <- n * p_hat^2
  discriminant <- B^2 - 4 * A * C
  if (discriminant < 0) stop("Discriminant is negative, no real solutions.")
  lower_bound <- (-B - sqrt(discriminant)) / (2 * A)
  upper_bound <- (-B + sqrt(discriminant)) / (2 * A)
  return(c(lower_bound, upper_bound, upper_bound - lower_bound))
}

# change parameters for the replication of this paper or for other studies
n <- 1000  
ps <- c(0.1, 0.2, 0.5, 0.8)  
num_simulations <- 5000  
alpha <- 0.05  

simulation_p_hat <- list()
simulation_results_no_dp <- list()

for (p in ps) {
  cat("\nRunning simulations without DP for p =", p, "\n")
  
  wald_covered <- 0
  wilson_covered <- 0
  wald_out_of_bounds <- 0  
  wilson_out_of_bounds <- 0  
  wald_lengths <- numeric(num_simulations)
  wilson_lengths <- numeric(num_simulations)
  
  for (i in 1:num_simulations) {
    p_hat <- rbinom(1, size = n, prob = p) / n
    simulation_p_hat[[paste0("p_", p, "_sim_", i)]] <- p_hat
    wald_ci <- wald_confidence_interval_no_dp(p_hat, n, alpha)
    wald_lengths[i] <- wald_ci[3]
    if (wald_ci[1] <= p && p <= wald_ci[2]) {
      wald_covered <- wald_covered + 1
    }
    
    if (wald_ci[1] < 0 || wald_ci[2] > 1) {
      wald_out_of_bounds <- wald_out_of_bounds + 1
    }
    
    wilson_ci <- wilson_confidence_interval_no_dp(p_hat, n, alpha)
    wilson_lengths[i] <- wilson_ci[3]
    if (wilson_ci[1] <= p && p <= wilson_ci[2]) {
      wilson_covered <- wilson_covered + 1
    }
    
    if (wilson_ci[1] < 0 || wilson_ci[2] > 1) {
      wilson_out_of_bounds <- wilson_out_of_bounds + 1
    }
  }
  
  wald_coverage <- wald_covered / num_simulations
  wilson_coverage <- wilson_covered / num_simulations
  avg_wald_length <- mean(wald_lengths)
  avg_wilson_length <- mean(wilson_lengths)
  
  simulation_results_no_dp[[paste0("p_", p)]] <- list(
    wald_coverage = wald_coverage,
    wilson_coverage = wilson_coverage,
    avg_wald_length = avg_wald_length,
    avg_wilson_length = avg_wilson_length,
    wald_out_of_bounds_percentage = wald_out_of_bounds / num_simulations,
    wilson_out_of_bounds_percentafe = wilson_out_of_bounds / num_simulations
  )
}

cat("\nChunk 1 completed: Simulations without DP.\n")
```

```{r}
coverage_results_no_dp <- data.frame()

for (p in ps) {
  result <- simulation_results_no_dp[[paste0("p_", p)]]
  coverage_results_no_dp <- rbind(coverage_results_no_dp, 
                                  data.frame(p = p,
                                             Wald_Coverage = result$wald_coverage,
                                             Wilson_Coverage = result$wilson_coverage,
                                             Avg_Wald_Length = result$avg_wald_length,
                                             Avg_Wilson_Length = result$avg_wilson_length,
                                             Wald_Out_Of_Bounds = result$wald_out_of_bounds,
                                             Wilson_Out_Of_Bounds = result$wilson_out_of_bounds))
}

cat("\nCoverage, Interval Lengths, and Out-of-Bounds Results for no DP:\n")
print(coverage_results_no_dp)

cat("\nExample of Wald and Wilson bounds for no DP:\n")

for (p in c(0.1, 0.5)) {
  cat("\nBounds for p =", p, ":\n")
  
  cat("Wald Bounds:\n")
  for (i in 1:5) {
    p_hat <- simulation_p_hat[[paste0("p_", p, "_sim_", i)]]
    
    wald_ci <- wald_confidence_interval_no_dp(p_hat, n, alpha = 0.05)
    
    cat("Simulation", i, " - p_hat:", p_hat, 
        "Lower Bound:", wald_ci[1], 
        "Upper Bound:", wald_ci[2], "\n")
  }
  
  cat("Wilson Bounds:\n")
  for (i in 1:5) {
    p_hat <- simulation_p_hat[[paste0("p_", p, "_sim_", i)]]
    wilson_ci <- wilson_confidence_interval_no_dp(p_hat, n, alpha = 0.05)
    cat("Simulation", i, " - p_hat:", p_hat, 
        "Lower Bound:", wilson_ci[1], 
        "Upper Bound:", wilson_ci[2], "\n")
  }
}

```


### Wald and Wilson with Differential Privacy(DP)

```{r cache=TRUE}
library(VGAM)    # the package is needed to generate Laplace noise; rlaplace()
set.seed(12345)  

simulate_noisy_proportion <- function(p_hat, n, epsilon) {
  laplace_noise <- rlaplace(1, location = 0, scale = 1 / (n * epsilon))  
  p_hat_star <- p_hat + laplace_noise
  p_hat_star <- pmax(0, pmin(1, p_hat_star)) # needed, otherwise square root can't be solved!
  return(p_hat_star)
}

wald_confidence_interval_dp <- function(p_hat_star, n, epsilon, alpha = 0.05) {
  z_alpha <- qnorm(1 - alpha / 2)  
  var_p_hat_star <- (p_hat_star * (1 - p_hat_star)) / n + 2 / (n^2 * epsilon^2)
  lower_bound <- p_hat_star - z_alpha * sqrt(var_p_hat_star)
  upper_bound <- p_hat_star + z_alpha * sqrt(var_p_hat_star)
  return(c(lower_bound, upper_bound, upper_bound - lower_bound))
}

wilson_confidence_interval_dp <- function(p_hat_star, n, epsilon, alpha = 0.05) {
  z_alpha <- qnorm(1 - alpha / 2) 
  A <- n + z_alpha^2
  B <- -(2 * n * p_hat_star + z_alpha^2)
  C <- n * p_hat_star^2 - (2 * z_alpha^2) / (n * epsilon^2)
  discriminant <- B^2 - 4 * A * C
  if (discriminant < 0) stop("Discriminant is negative, no real solutions.")
  lower_bound <- (-B - sqrt(discriminant)) / (2 * A)
  upper_bound <- (-B + sqrt(discriminant)) / (2 * A)
  return(c(lower_bound, upper_bound, upper_bound - lower_bound))
}

# change parameters for the replication of this paper or for other studies
n <- 1000 
ps <- c(0.1, 0.2, 0.5, 0.8)  
epsilons <- c(0.1, 0.3, 0.5, 5)  
num_simulations <- 5000  
alpha <- 0.05  


simulation_results_with_dp <- list()
stored_p_hat_star <- list()  

for (epsilon in epsilons) {
  for (p in ps) {
    cat("\nRunning simulations with DP for Epsilon =", epsilon, ", p =", p, "\n")
    
    wald_covered_dp <- 0
    wilson_covered_dp <- 0
    wald_out_of_bounds <- 0
    wilson_out_of_bounds <- 0
    wald_lengths_dp <- numeric(num_simulations)
    wilson_lengths_dp <- numeric(num_simulations)
    wald_bounds_dp <- data.frame(Lower = numeric(num_simulations), Upper = numeric(num_simulations))
    wilson_bounds_dp <- data.frame(Lower = numeric(num_simulations), Upper = numeric(num_simulations))
    
    p_hat_star_list <- numeric(num_simulations)  
    
    for (i in 1:num_simulations) {
      p_hat <- simulation_p_hat[[paste0("p_", p, "_sim_", i)]]
      
      p_hat_star <- simulate_noisy_proportion(p_hat, n, epsilon)
      p_hat_star_list[i] <- p_hat_star
      
      wald_ci_dp <- wald_confidence_interval_dp(p_hat_star, n, epsilon, alpha)
      wald_lengths_dp[i] <- wald_ci_dp[3]
      wald_bounds_dp$Lower[i] <- wald_ci_dp[1]
      wald_bounds_dp$Upper[i] <- wald_ci_dp[2]
      if (wald_ci_dp[1] <= p && p <= wald_ci_dp[2]) {
        wald_covered_dp <- wald_covered_dp + 1
      }
      if (wald_ci_dp[1] < 0 || wald_ci_dp[2] > 1) {
        wald_out_of_bounds <- wald_out_of_bounds + 1
      }
      
      wilson_ci_dp <- wilson_confidence_interval_dp(p_hat_star, n, epsilon, alpha)
      wilson_lengths_dp[i] <- wilson_ci_dp[3]
      wilson_bounds_dp$Lower[i] <- wilson_ci_dp[1]
      wilson_bounds_dp$Upper[i] <- wilson_ci_dp[2]
      if (wilson_ci_dp[1] <= p && p <= wilson_ci_dp[2]) {
        wilson_covered_dp <- wilson_covered_dp + 1
      }
      if (wilson_ci_dp[1] < 0 || wilson_ci_dp[2] > 1) {
        wilson_out_of_bounds <- wilson_out_of_bounds + 1
      }
    }
    
    stored_p_hat_star[[paste0("Epsilon_", epsilon, "_p_", p)]] <- p_hat_star_list
    
    wald_coverage_dp <- wald_covered_dp / num_simulations
    wilson_coverage_dp <- wilson_covered_dp / num_simulations
    avg_wald_length_dp <- mean(wald_lengths_dp)
    avg_wilson_length_dp <- mean(wilson_lengths_dp)
    
    simulation_results_with_dp[[paste0("Epsilon_", epsilon, "_p_", p)]] <- list(
      wald_coverage_dp = wald_coverage_dp,
      wilson_coverage_dp = wilson_coverage_dp,
      avg_wald_length_dp = avg_wald_length_dp,
      avg_wilson_length_dp = avg_wilson_length_dp,
      wald_bounds = wald_bounds_dp,
      wilson_bounds = wilson_bounds_dp,
      wald_out_of_bounds = wald_out_of_bounds / num_simulations,
      wilson_out_of_bounds = wilson_out_of_bounds / num_simulations
    )
  }
}

cat("\nChunk 2 completed: Simulations with DP.\n")
```

```{r}
coverage_results_dp <- data.frame()

for (epsilon in epsilons) {
  for (p in ps) {
    result <- simulation_results_with_dp[[paste0("Epsilon_", epsilon, "_p_", p)]]
    coverage_results_dp <- rbind(coverage_results_dp, 
                                 data.frame(Epsilon = epsilon, 
                                            p = p,
                                            Wald_Coverage = result$wald_coverage_dp,
                                            Wilson_Coverage = result$wilson_coverage_dp,
                                            Avg_Wald_Length = result$avg_wald_length_dp,
                                            Avg_Wilson_Length = result$avg_wilson_length_dp,
                                            Wald_Out_Of_Bounds = result$wald_out_of_bounds,
                                            Wilson_Out_Of_Bounds = result$wilson_out_of_bounds))
  }
}

cat("\nCoverage, Interval Length, and Out-of-Bounds Results for DP:\n")
print(coverage_results_dp)

cat("\nExample of Wald and Wilson bounds for DP:\n")

for (epsilon in c(0.1, 0.5)) {
  for (p in c(0.1, 0.5)) {
    result <- simulation_results_with_dp[[paste0("Epsilon_", epsilon, "_p_", p)]]
    
    cat("\nBounds for Epsilon =", epsilon, ", p =", p, ":\n")
    
    cat("Wald Bounds:\n")
    print(head(result$wald_bounds))
    
    cat("Wilson Bounds:\n")
    print(head(result$wilson_bounds))
    
    cat("Wald out of Bounds:\n")
    print(head(result$wald_out_of_bounds))
    
    cat("Wilson out of Bounds:\n")
    print(head(result$wilson_out_of_bounds))
  }
}
```

### Bayesian Credible Interval(Flat Prior (Uniform))


```{r cache=TRUE}
sample_phat_from_grid <- function(phat_star, n, epsilon, q) {
  b <- 1 / (n * epsilon)
  grid <- seq(0, 1, by = 1/n)  
  
  likelihoods <- exp(-abs(phat_star - grid) / b) * dbinom(grid * n, n, q)
  
  # safety check: fall back to phat_star if all likelihoods are zero/NA
  if (all(is.na(likelihoods)) || sum(likelihoods, na.rm = TRUE) == 0) {
    return(phat_star)
  }
  
  likelihoods <- likelihoods / sum(likelihoods)
  
  sampled_phat <- sample(grid, size = 1, prob = likelihoods)
  
  return(sampled_phat)
}

gibbs_sampling_grid <- function(phat_star, n, epsilon, iterations = 5000) {
  p_samples <- numeric(iterations)
  p_samples[1] <- 0.5
  for (i in 2:iterations) {
    p <- p_samples[i - 1]
    phat <- sample_phat_from_grid(phat_star, n, epsilon, p)
    alpha <- phat * n + 1
    beta <- (1 - phat) * n + 1
    if (alpha <= 0 || beta <= 0) {
      p_samples[i] <- p_samples[i - 1]
    } else {
      p_samples[i] <- rbeta(1, alpha, beta) 
    }
  }
  
  return(p_samples)
}

credible_interval <- function(posterior_samples, alpha = 0.05) {
  posterior_samples <- posterior_samples[!is.na(posterior_samples)]
  lower_bound <- quantile(posterior_samples, probs = alpha / 2)
  upper_bound <- quantile(posterior_samples, probs = 1 - alpha / 2)
  return(c(lower_bound, upper_bound))
}

# change parameters for the replication of this paper or for other studies
n <- 1000 
ps <- c(0.1, 0.2, 0.5, 0.8)  
epsilons <- c(0.1, 0.3, 0.5, 5)  
num_simulations <- 5000  
alpha <- 0.05 

bayesian_simulation_results <- list()
set.seed(12345)
for (p_idx in 1:length(ps)) {
  p_true <- ps[p_idx]
  
  for (eps_idx in 1:length(epsilons)) {
    epsilon <- epsilons[eps_idx]
    cat("\nProcessing: Epsilon =", epsilon, "and p =", p_true, "\n")
    count_in_interval <- 0
    credible_intervals <- matrix(NA, nrow = num_simulations, ncol = 2)
    for (sim in 1:num_simulations) {
      phat <- sum(rbinom(n, 1, p_true)) / n  
      laplace_noise <- rlaplace(1, location = 0, scale = 1 / (n * epsilon))
      phat_star <- phat + laplace_noise 
      posterior_samples <- gibbs_sampling_grid(phat_star, n, epsilon, iterations = 5000)
      ci <- credible_interval(posterior_samples, alpha = 0.05)
      credible_intervals[sim, ] <- ci
      if (p_true >= ci[1] && p_true <= ci[2]) {
        count_in_interval <- count_in_interval + 1
      }
    }
    
    bayesian_simulation_results[[paste0("Epsilon_", epsilon, "_p_", p_true)]] <- list(
      bayesian_coverage = count_in_interval / num_simulations,
      credible_intervals = credible_intervals
    )
    
    cat("Completed: Epsilon =", epsilon, "and p =", p_true, "\n")
  }
}
```


```{r}
bayesian_coverage_results <- data.frame()

for (epsilon in epsilons) {
  for (p in ps) {
    result <- bayesian_simulation_results[[paste0("Epsilon_", epsilon, "_p_", p)]]
    bayesian_coverage <- result$bayesian_coverage
    lower_bound <- result$credible_intervals[1, 1]  
    upper_bound <- result$credible_intervals[1, 2]  
    avg_length <- mean(result$credible_intervals[, 2] - result$credible_intervals[, 1])  
    bayesian_coverage_results <- rbind(bayesian_coverage_results, 
                                       data.frame(Epsilon = epsilon, 
                                                  p = p, 
                                                  Bayesian_Coverage = bayesian_coverage, 
                                                  Lower_Bound = lower_bound, 
                                                  Upper_Bound = upper_bound,
                                                  Avg_Length = avg_length))
  }
}

cat("\nBayesian Coverage, Interval Bounds, and Average Length Results:\n")
print(bayesian_coverage_results)

cat("\nExample of Detailed Results for Selected Epsilon and p:\n")

for (epsilon in c(0.1, 0.5)) {
  for (p in c(0.1, 0.5)) {
    result <- bayesian_simulation_results[[paste0("Epsilon_", epsilon, "_p_", p)]]
    
    avg_length <- mean(result$credible_intervals[, 2] - result$credible_intervals[, 1])
    
    cat("\nEpsilon =", epsilon, ", p =", p, ":\n")
    cat("Bayesian Coverage:", result$bayesian_coverage, "\n")
    cat("First Credible Interval: [", result$credible_intervals[1, 1], ", ", result$credible_intervals[1, 2], "]\n")
    cat("Average Length of Credible Intervals:", avg_length, "\n")
  }
}
```

### Bayesian Credible Interval(Jeffreys Prior)

```{r cache=TRUE}
library(VGAM)   
library(ggplot2) 

sample_phat_from_grid <- function(phat_star, n, epsilon, q) {
  b <- 1 / (n * epsilon)
  grid <- seq(0, 1, by = 1/n) 
  
  likelihoods <- exp(-abs(phat_star - grid) / b) * dbinom(grid * n, n, q)
  
  # safety check: fall back to phat_star if all likelihoods are zero/NA
  if (all(is.na(likelihoods)) || sum(likelihoods, na.rm = TRUE) == 0) {
    return(phat_star)
  }
  
  likelihoods <- likelihoods / sum(likelihoods)
  sampled_phat <- sample(grid, size = 1, prob = likelihoods)
  
  return(sampled_phat)
}

gibbs_sampling_grid <- function(phat_star, n, epsilon, iterations = 5000) {
  p_samples <- numeric(iterations)
  p_samples[1] <- 0.5
  for (i in 2:iterations) {
    p <- p_samples[i - 1]
    phat <- sample_phat_from_grid(phat_star, n, epsilon, p)
    alpha <- phat * n + 0.5  # Jeffreys Prior: Beta(1/2, 1/2)
    beta <- (1 - phat) * n + 0.5
    
    if (alpha <= 0 || beta <= 0) {
      p_samples[i] <- p_samples[i - 1]
    } else {
      p_samples[i] <- rbeta(1, alpha, beta) 
    }
  }
  
  return(p_samples)
}

credible_interval <- function(posterior_samples, alpha = 0.05) {
  posterior_samples <- posterior_samples[!is.na(posterior_samples)]  
  lower_bound <- quantile(posterior_samples, probs = alpha / 2)
  upper_bound <- quantile(posterior_samples, probs = 1 - alpha / 2)
  return(c(lower_bound, upper_bound))
}

# change parameters for the replication of this paper or for other studies
n <- 1000  
ps <- c(0.1, 0.2, 0.5, 0.8)  
epsilons <- c(0.1, 0.3, 0.5, 5)  
num_simulations <- 5000  
alpha <- 0.05 

bayesian_simulation_results <- list()
set.seed(12345)
for (p_idx in 1:length(ps)) {
  p_true <- ps[p_idx]
  
  for (eps_idx in 1:length(epsilons)) {
    epsilon <- epsilons[eps_idx]
    
    cat("\nProcessing: Epsilon =", epsilon, "and p =", p_true, "\n")
    count_in_interval <- 0
    credible_intervals <- matrix(NA, nrow = num_simulations, ncol = 2)
    for (sim in 1:num_simulations) {
      phat <- sum(rbinom(n, 1, p_true)) / n  
      laplace_noise <- rlaplace(1, location = 0, scale = 1 / (n * epsilon))
      phat_star <- phat + laplace_noise
      posterior_samples <- gibbs_sampling_grid(phat_star, n, epsilon, iterations = 5000)
      ci <- credible_interval(posterior_samples, alpha = 0.05)
      credible_intervals[sim, ] <- ci
      if (p_true >= ci[1] && p_true <= ci[2]) {
        count_in_interval <- count_in_interval + 1
      }
    }
    bayesian_simulation_results[[paste0("Epsilon_", epsilon, "_p_", p_true)]] <- list(
      bayesian_coverage = count_in_interval / num_simulations,
      credible_intervals = credible_intervals
    )
    cat("Completed: Epsilon =", epsilon, "and p =", p_true, "\n")
  }
}

bayesian_coverage_results <- data.frame()
for (epsilon in epsilons) {
  for (p in ps) {
    result <- bayesian_simulation_results[[paste0("Epsilon_", epsilon, "_p_", p)]]
    bayesian_coverage <- result$bayesian_coverage
    lower_bound <- result$credible_intervals[1, 1]  
    upper_bound <- result$credible_intervals[1, 2]  
    avg_length <- mean(result$credible_intervals[, 2] - result$credible_intervals[, 1]) 
    bayesian_coverage_results <- rbind(bayesian_coverage_results, 
                                       data.frame(Epsilon = epsilon, 
                                                  p = p, 
                                                  Bayesian_Coverage = bayesian_coverage, 
                                                  Lower_Bound = lower_bound, 
                                                  Upper_Bound = upper_bound,
                                                  Avg_Length = avg_length))
  }
}
```

```{r}
cat("\nBayesian Coverage, Interval Bounds, and Average Length Results:\n")
print(bayesian_coverage_results)
cat("\nExample of Detailed Results for Selected Epsilon and p:\n")
for (epsilon in c(0.1, 0.5)) {
  for (p in c(0.1, 0.5)) {
    result <- bayesian_simulation_results[[paste0("Epsilon_", epsilon, "_p_", p)]]
    avg_length <- mean(result$credible_intervals[, 2] - result$credible_intervals[, 1])
    cat("\nEpsilon =", epsilon, ", p =", p, ":\n")
    cat("Bayesian Coverage:", result$bayesian_coverage, "\n")
    cat("First Credible Interval: [", result$credible_intervals[1, 1], ", ", result$credible_intervals[1, 2], "]\n")
    cat("Average Length of Credible Intervals:", avg_length, "\n")
  }
}
```


### Exact Interval

```{r cache=TRUE}
library(VGAM)

# change parameters for the replication of this paper or for other studies
set.seed(12345)
n <- 1000                               
epsilons <- c(0.1, 0.3, 0.5, 5)        
ps <- c(0.1, 0.2, 0.5, 0.8)             
alpha <- 0.05                           
num_simulations <- 5000             
n_cover_sims <- 5000                  

rlaplace <- function(n, location = 0, scale = 1) {
  u <- runif(n, min = -0.5, max = 0.5)
  location - scale * sign(u) * log(1 - 2 * abs(u))
}

coverage_results <- data.frame()

for (epsilon in epsilons) {
  for (p_true in ps) {
    cat("Processing Epsilon =", epsilon, ", p_true =", p_true, "\n")
    
    lambda <- 1 / (n * epsilon)
    
    upper_tail_prob <- function(p, p_hat_star_obs) {
      p <- min(max(p, 0), 1)  #helper for unitroot() to find the correct regiion [0,1]
      X_sim <- rbinom(num_simulations, n, p)
      p_hat_sim <- X_sim / n
      eta_sim <- rlaplace(num_simulations, 0, lambda)
      p_hat_star_sim <- p_hat_sim + eta_sim
      mean(p_hat_star_sim >= p_hat_star_obs, na.rm = TRUE)
    }
    
    lower_tail_prob <- function(p, p_hat_star_obs) {
      p <- min(max(p, 0), 1)
      X_sim <- rbinom(num_simulations, n, p)
      p_hat_sim <- X_sim / n
      eta_sim <- rlaplace(num_simulations, 0, lambda)
      p_hat_star_sim <- p_hat_sim + eta_sim
      mean(p_hat_star_sim <= p_hat_star_obs, na.rm = TRUE)
    }
    
    cover_count <- 0
    interval_lengths <- numeric(n_cover_sims)
    
    for (k in 1:n_cover_sims) {
      X_obs <- rbinom(1, n, p_true)
      p_hat_obs <- X_obs / n
      eta <- rlaplace(1, 0, lambda)
      p_hat_star_obs <- p_hat_obs + eta
      
      p_L <- tryCatch({
        uniroot(function(p) upper_tail_prob(p, p_hat_star_obs) - alpha/2,
                lower = 0, upper = p_hat_star_obs, tol = 1e-4)$root
      }, error = function(e) 0)
      
      p_U <- tryCatch({
        uniroot(function(p) lower_tail_prob(p, p_hat_star_obs) - alpha/2,
                lower = p_hat_star_obs, upper = 1, tol = 1e-4)$root
      }, error = function(e) 1)
      
      if (p_true >= p_L && p_true <= p_U) {
        cover_count <- cover_count + 1
      }
      
      interval_lengths[k] <- p_U - p_L
    }
    
    coverage_est <- cover_count / n_cover_sims
    avg_length <- mean(interval_lengths)
    
    cat("Coverage =", round(coverage_est, 3),
        "Avg interval length =", round(avg_length, 3), "\n\n")
    
    coverage_results <- rbind(coverage_results,
                              data.frame(epsilon = epsilon,
                                         p_true = p_true,
                                         coverage = coverage_est,
                                         avg_length = avg_length))
  }
}

print(coverage_results)
```



### Plots n = 100

#### Data n =100, make sure n=100 in all above code, the result is extracted from setting n=100 above.
```{r}
df <- data.frame(
  epsilon = rep(c(0.1, 0.3, 0.5, 5.0), each = 4 * 3),
  p = rep(rep(c(0.1, 0.2, 0.5, 0.8), each = 3), times = 4),
  method = rep(c("Bayes-U", "Bayes-J", "Exact"), times = 16),
  coverage = c(
    # ε = 0.1
    95.5, 98.1, 97.6,
    97.0, 97.9, 97.5,
    95.2, 93.8, 96.0,
    96.6, 98.1, 97.3,
    # ε = 0.3
    97.0, 95.7, 97.2,
    95.4, 94.5, 95.3,
    94.8, 95.0, 95.1,
    94.9, 94.0, 95.4,
    # ε = 0.5
    95.2, 93.2, 95.8,
    95.0, 94.7, 95.6,
    95.5, 95.0, 94.9,
    95.0, 95.2, 95.5,
    # ε = 5.0
    94.3, 95.4, 95.3,
    94.6, 95.0, 95.0,
    94.6, 94.9, 95.0,
    95.0, 94.5, 95.2
  ),
  length = c(
    # ε = 0.1
    0.44, 0.40, 0.56,
    0.48, 0.49, 0.55,
    0.56, 0.65, 0.61,
    0.48, 0.49, 0.55,
    # ε = 0.3
    0.20, 0.20, 0.24,
    0.24, 0.25, 0.24,
    0.27, 0.27, 0.27,
    0.24, 0.25, 0.25,
    # ε = 0.5
    0.16, 0.16, 0.17,
    0.19, 0.19, 0.19,
    0.22, 0.22, 0.22,
    0.19, 0.19, 0.19,
    # ε = 5.0
    0.12, 0.12, 0.12,
    0.15, 0.15, 0.16,
    0.19, 0.19, 0.19,
    0.15, 0.15, 0.16
  )
)

waldwilson_n_100 <- data.frame(
  epsilon = rep(c(0.1, 0.3, 0.5, 5.0), each = 4 * 2),
  p = rep(rep(c(0.1, 0.2, 0.5, 0.8), each = 2), times = 4),
  method = rep(c("Wald-DP", "Wilson-DP"), times = 16),
  coverage = c(
    # ε = 0.1
    95.9, 95.5,
    94.8, 94.6,
    93.5, 93.9,
    97.3, 97.2,
    # ε = 0.3
    93.7, 97.2,
    93.9, 94.4,
    94.4, 94.8,
    93.8, 94.6,
    # ε = 0.5
    93.5, 95.0,
    94.1, 94.5,
    94.3, 94.6,
    94.3, 95.2,
    # ε = 5.0
    92.9, 94.7,
    94.0, 94.8,
    94.4, 94.7,
    93.5, 94.7
  ),
  length = c(
    # ε = 0.1
    0.567, 0.557,
    0.574, 0.564,
    0.585, 0.574,
    0.574, 0.564,
    # ε = 0.3
    0.218, 0.216,
    0.241, 0.237,
    0.268, 0.263,
    0.241, 0.237,
    # ε = 0.5
    0.160, 0.160,
    0.191, 0.189,
    0.224, 0.220,
    0.191, 0.189,
    # ε = 5.0
    0.116, 0.118,
    0.156, 0.155,
    0.195, 0.192,
    0.156, 0.155
  )
)

df_full_n_100 <- rbind(df, waldwilson_n_100)
```

#### Final plot for n=100
```{r}
library(ggplot2)
library(cowplot)

method_colors <- c(
  "Wald-DP"   = "#D55E00",
  "Wilson-DP" = "#E69F00",
  "Bayes-U"        = "#0072B2",
  "Bayes-J"        = "#56B4E9",
  "Exact"          = "#009E73"
)

df_full_n_100$method <- factor(
  df_full_n_100$method,
  levels = c("Exact", "Bayes-U", "Bayes-J", "Wald-DP", "Wilson-DP")
)

add_vertical_lines <- function(plot) {
  plot + geom_vline(xintercept = 0.5, color = NA) +  
    theme(
      panel.border = element_blank(),
      axis.line.x = element_line(color = "black", linewidth = 0.28)
    ) +
    theme(
      panel.spacing.x = unit(1.5, "lines"),
      panel.grid = element_blank()
    ) +
    geom_segment(
      data = data.frame(x = Inf, y = -Inf),
      aes(x = -Inf, xend = -Inf, y = -Inf, yend = Inf),
      inherit.aes = FALSE,
      color = "black",
      linewidth = 0.6
    )
}

plot_coverage_n_100 <- ggplot(df_full_n_100, aes(
  x = factor(p),
  y = coverage,
  color = method,
  shape = method
)) +
  geom_point(size = 2) +
  facet_wrap(~epsilon, nrow = 1, labeller = label_bquote(epsilon == .(epsilon))) +
  scale_color_manual(values = method_colors) +
  scale_shape_manual(values = c(15, 16, 17, 18, 8, 3)) +
  labs(x = NULL, y = "Coverage (%)", color = "Method", shape = "Method") +
  theme_minimal() +
  theme(
    legend.position = "none",
    strip.text = element_text(size = 11, face = "bold"),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.x = element_blank(),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 11),
    panel.grid = element_blank(),
    panel.spacing.x = unit(1.5, "lines")
  )

plot_coverage_n_100 <- add_vertical_lines(plot_coverage_n_100)

plot_length_n_100 <- ggplot(df_full_n_100, aes(
  x = factor(p),
  y = length,
  color = method,
  shape = method
)) +
  geom_point(size = 2) +
  facet_wrap(~epsilon, nrow = 1, labeller = label_bquote("")) +
  scale_color_manual(values = method_colors) +
  scale_shape_manual(values = c(15, 16, 17, 18, 8, 3)) +
  labs(x = "True Proportion (p)", y = "Interval Length", color = "Method", shape = "Method") +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    legend.title = element_text(face = "bold"),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 11, face = "bold"),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 11),
    panel.grid = element_blank(),
    panel.spacing.x = unit(1.5, "lines")
  )

plot_length_n_100 <- add_vertical_lines(plot_length_n_100)

final_plot_n_100 <- plot_grid(
  plot_coverage_n_100,
  plot_length_n_100,
  ncol = 1,
  align = "v",
  axis = "lr",
  rel_heights = c(1, 1)
)

final_plot_n_100
ggsave("Coverage_Length_Combined_n_100.png", final_plot_n_100, width = 12, height = 7, dpi = 600)
```

### Plots n = 1000

#### Data n = 1000, extracted from the result above
```{r}
df_n_1000 <- data.frame(
  epsilon = rep(c(0.1, 0.3, 0.5, 5.0), each = 4 * 3),
  p = rep(rep(c(0.1, 0.2, 0.5, 0.8), each = 3), times = 4),
  method = rep(c("Bayes-U", "Bayes-J", "Exact"), times = 16),
  coverage = c(
    # ε = 0.1
    95.5, 95.3, 94.8,
    94.9, 95.5, 95.6,
    95.5, 94.9, 95.3,
    95.1, 95.1, 95.1,
    # ε = 0.3
    95.1, 95.1, 94.9,
    95.0, 94.8, 94.2,
    94.9, 95.4, 95.0,
    95.0, 95.1, 95.1,
    # ε = 0.5
    95.2, 94.9, 94.5,
    95.0, 95.2, 95.1,
    94.8, 95.1, 94.6,
    95.1, 95.0, 95.6,
    # ε = 5.0
    95.0, 95.0, 94.4,
    95.0, 94.9, 95.1,
    95.2, 95.1, 95.2,
    94.7, 94.9, 95.5
  ),
  length = c(
    # ε = 0.1
    0.07, 0.07, 0.07,
    0.08, 0.08, 0.08,
    0.08, 0.08, 0.08,
    0.08, 0.08, 0.08,
    # ε = 0.3
    0.04, 0.04, 0.04,
    0.05, 0.05, 0.05,
    0.06, 0.06, 0.06,
    0.05, 0.05, 0.05,
    # ε = 0.5
    0.04, 0.04, 0.04,
    0.05, 0.05, 0.05,
    0.06, 0.06, 0.06,
    0.05, 0.05, 0.05,
    # ε = 5.0
    0.04, 0.04, 0.04,
    0.05, 0.05, 0.05,
    0.06, 0.06, 0.06,
    0.05, 0.05, 0.05
  )
)

waldwilson_n_1000 <- data.frame(
  epsilon = rep(c(0.1, 0.3, 0.5, 5.0), each = 4 * 2),
  p = rep(rep(c(0.1, 0.2, 0.5, 0.8), each = 2), times = 4),
  method = rep(c("Wald-DP", "Wilson-DP"), times = 16),
  coverage = c(
    # ε = 0.1
    94.72, 94.48,
    94.80, 94.76,
    95.02, 95.06,
    94.68, 94.70,
    # ε = 0.3
    95.08, 95.08,
    94.62, 94.60,
    94.98, 95.02,
    95.38, 95.30,
    # ε = 0.5
    95.06, 95.08,
    94.62, 94.52,
    94.92, 94.94,
    95.16, 95.20,
    # ε = 5.0
    95.08, 95.06,
    94.76, 94.58,
    95.00, 95.04,
    95.40, 95.28
  ),
  length = c(
    # ε = 0.1
    0.067, 0.067,
    0.074, 0.074,
    0.083, 0.083,
    0.074, 0.074,
    # ε = 0.3
    0.041, 0.042,
    0.053, 0.053,
    0.065, 0.065,
    0.053, 0.053,
    # ε = 0.5
    0.039, 0.039,
    0.051, 0.051,
    0.063, 0.063,
    0.051, 0.051,
    # ε = 5.0
    0.037, 0.037,
    0.050, 0.050,
    0.062, 0.062,
    0.050, 0.050
  )
)

df_full_n_1000 <- rbind(df_n_1000, waldwilson_n_1000)
```

#### Final plot for n=1000
```{r}
library(ggplot2)
library(cowplot)

method_colors <- c(
  "Wald-DP"   = "#D55E00",
  "Wilson-DP" = "#E69F00",
  "Bayes-U"        = "#0072B2",
  "Bayes-J"        = "#56B4E9",
  "Exact"          = "#009E73"
)

df_full_n_1000$method <- factor(
  df_full_n_1000$method,
  levels = c("Exact", "Bayes-U", "Bayes-J", "Wald-DP", "Wilson-DP")
)

add_vertical_lines <- function(plot) {
  plot + geom_vline(xintercept = 0.5, color = NA) +  # just to preserve structure
    theme(
      panel.border = element_blank(),
      axis.line.x = element_line(color = "black", linewidth = 0.28)
    ) +
    theme(
      panel.spacing.x = unit(1.5, "lines"),
      panel.grid = element_blank()
    ) +
    geom_segment(
      data = data.frame(x = Inf, y = -Inf),
      aes(x = -Inf, xend = -Inf, y = -Inf, yend = Inf),
      inherit.aes = FALSE,
      color = "black",
      linewidth = 0.6
    )
}

plot_coverage_n_1000 <- ggplot(df_full_n_1000, aes(
  x = factor(p),
  y = coverage,
  color = method,
  shape = method
)) +
  geom_point(size = 2) +
  facet_wrap(~epsilon, nrow = 1, labeller = label_bquote(epsilon == .(epsilon))) +
  scale_color_manual(values = method_colors) +
  scale_shape_manual(values = c(15, 16, 17, 18, 8, 3)) +
  labs(x = NULL, y = "Coverage (%)", color = "Method", shape = "Method") +
  theme_minimal() +
  theme(
    legend.position = "none",
    strip.text = element_text(size = 11, face = "bold"),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.x = element_blank(),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 11),
    panel.grid = element_blank(),
    panel.spacing.x = unit(1.5, "lines")
  )

plot_coverage_n_1000 <- add_vertical_lines(plot_coverage_n_1000)

# --- Length plot ---
plot_length_n_1000 <- ggplot(df_full_n_1000, aes(
  x = factor(p),
  y = length,
  color = method,
  shape = method
)) +
  geom_point(size = 2) +
  facet_wrap(~epsilon, nrow = 1, labeller = label_bquote("")) +
  scale_color_manual(values = method_colors) +
  scale_shape_manual(values = c(15, 16, 17, 18, 8, 3)) +
  labs(x = "True Proportion (p)", y = "Interval Length", color = "Method", shape = "Method") +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    legend.title = element_text(face = "bold"),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 11, face = "bold"),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 11),
    panel.grid = element_blank(),
    panel.spacing.x = unit(1.5, "lines")
  )

plot_length_n_1000 <- add_vertical_lines(plot_length_n_1000)

final_plot_n_1000 <- plot_grid(
  plot_coverage_n_1000,
  plot_length_n_1000,
  ncol = 1,
  align = "v",
  axis = "lr",
  rel_heights = c(1, 1)
)

final_plot_n_1000
ggsave("Coverage_Length_Combined_n_1000.png", final_plot_n_1000, width = 12, height = 7, dpi = 600)
```






